# Group 8 final project
Authors: Enrique Martinez, Bernat Godayol, Paula Molina, Sergio Esteban, Jakob Larsen.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
```
## ntroduction

This project used data from the 2020 paper from (authors) about gut microbiota populations in patients inoculated with a specific *E. coli* strain and then treated with two diferent antibiotics.
## The data

The data was stored in 3 diferent files:

*   **ctu_counts**: A .csv file containing information about the abundance of *E. coli* for each treatment.

```{r, echo = FALSE, message = FALSE}
raw_cfu_counts <- read_csv("_raw/cfu_counts.csv")
raw_cfu_counts
```
*   **mapfile**: Metadata mapping file containing sequencing and experimental information for each sample.
```{r, echo = FALSE, message = FALSE}
map_df_cols <- read_lines("_raw/mapfile.txt",n_max=1) %>%
  str_split("\\t",simplify = TRUE)

map_df <- read_lines("_raw/mapfile.txt", skip=1, skip_empty_rows = TRUE) %>%
  as_tibble_col(column_name = "lines") %>%
  separate(lines,map_df_cols,sep="\\t")

map_df
```
*   **otufile**: OTU abundance and taxonomic identification file.
```{r}
otu_df_cols <- read_lines("_raw/otufile.txt",n_max=1) %>%
  str_split("\\t",simplify = TRUE)

otu_df <- read_lines("_raw/otufile.txt",skip=1,skip_empty_rows = TRUE) %>%
  as_tibble_col(column_name = "lines") %>%
  separate(lines,otu_df_cols,sep="\\t")

otu_df
```

## Tidying the data
